Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Discussing stuff

As a result, we got the following table:

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
FIRSTCOUSIN        & 695             & 2,02                \\ \hline
SUPERCLASS         & 488             & 1,42                \\ \hline
COMMONHIERARCHY    & 442             & 1,29                \\ \hline
UNRELATED          & 13537           & 39,39               \\ \hline
EXTERNALSUPERCLASS & 2402            & 6,99                \\ \hline
SIBLING            & 5978            & 17,39               \\ \hline
SAMEMETHOD         & 2456            & 7,15                \\ \hline
SAMECLASS          & 8341            & 24,27               \\ \hline
ANCESTOR           & 28              & 0,08               \\ \hline
\end{tabular}
\end{table}

%TODO: Add and discuss measurements

@@

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
METHODLEVEL       & 19817           & 57,66               \\ \hline
CLASSLEVEL        & 14366           & 41,80               \\ \hline
INTERFACELEVEL    & 110             & 0,32                \\ \hline
ENUMLEVEL         & 74              & 0,22                \\ \hline
\end{tabular}
\end{table}
%TODO: Add and discuss measurements

>>>>

The table below shows our results.

\begin{table}[H]
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13537           & 39,39               \\ \hline
Same Class          & 8341            & 24,27               \\ \hline
Sibling            & 5978            & 17,39               \\ \hline
Same Method         & 2456            & 7,15                \\ \hline
External Superclass & 2402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{table}

Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass). On the second place, we have the ``Same Class'' clones. On the third place come the ``Sibling'' clones.

@@

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size). We set out to test this for ourselves on our corpus, and got the following results:

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
Method Level       & 19817           & 57,66               \\ \hline
Class Level        & 14366           & 41,80               \\ \hline
Interface Level    & 110             & 0,32                \\ \hline
Enum Level         & 74              & 0,22                \\ \hline
\end{tabular}
\end{table}
%TODO: Add and discuss measurements
